Summarize twas: chr17 to 22

### 2020-09-14 analysis/simulation-multi-ukbchr17to22-gtex.adipose_susieprior.Rmd
susieI plots

# Simulation 1-x, setting 1
- filter criteria: rpip 0.3 and causal

@@

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for regions with mr.ash2 regional PIP > 0.5.

@@

# simulation 1-x, setting 2
- filter criteria: rpip 0.3

@@

We run 50 simulations and run susie using different priors and `L= 1`. We apply susie for all regions.

@@

# Simulation 3-x, setting 1
- filter criteria: rpip 0.3 and causal

@@

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for regions with mr.ash2 regional PIP > 0.5.

@@

# Simulation 3-x, setting 2
- filter criteria: rpip 0.3

@@

We run 100 simulations and run susie using different priors and `L= 1`. We only apply susie for regions with mr.ash2 regional PIP > 0.5.

>>>>

# Simulation 1-x, setting 1

@@

We run 100 simulations and run susie using priors obtained from susieI. Two examples are shown. The setting is the same as in [here](https://stephenslab.github.io/causal-TWAS/simulation-susieI-ukbchr17to22-gtex.adipose.html#regions:_causal). Regions are rpip from mr.ash2 > 0.3 and causal. We take simulation setting 1-x.

@@

# simulation 1-x, setting 2

@@

We run 100 simulations and run susie using priors obtained from susieI. Two examples are shown. The setting is the same as in [here](https://stephenslab.github.io/causal-TWAS/simulation-susieI-ukbchr17to22-gtex.adipose.html#regions:_mrash_gene+snp_(1)). Regions are rpip from mr.ash2 > 0.3. We take simulation setting 1-x.

@@

# Simulation 3-x, setting 1

@@

We run 100 simulations and run susie using priors obtained from susieI. Two examples are shown. The setting is the same as in [here](https://stephenslab.github.io/causal-TWAS/simulation-susieI-ukbchr17to22-gtex.adipose.html#regions:_causal). Regions are rpip from mr.ash2 > 0.3 and causal. We take simulation setting 3-x.

@@

# Simulation 3-x, setting 2

@@

We run 100 simulations and run susie using priors obtained from susieI. Two examples are shown. The setting is the same as in [here](https://stephenslab.github.io/causal-TWAS/simulation-susieI-ukbchr17to22-gtex.adipose.html#regions:_mrash_gene+snp_(1)). Regions are rpip from mr.ash2 > 0.3. We take simulation setting 1-x.
